SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-08 frontrunning/Latex/sections/paper.tex
make it almost 15 pages again.

The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables. Consider Cryptokitties\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}, the most active DApp in this category and third most active overall. Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain. They can be bought, sold, or bred with other cryptokitties. At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}\footnote{\url{https://ens.domains/}} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name, \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain in the auction. A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}. The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.

@@

By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario. As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to Status.im ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds back to these addresses, these funds were sent back to F2Pool main address a few days after and the tokens were aggregated later in one single address. Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} and gain monetary profit.

@@

In the finance literature, Malinova and Park discuss front-running mitigations for blockchain-based trading platforms~\cite{malinova2017market}. Instead of studying DApps, they develop an economic model where transactions, asset holdings, and traders' identities have greater transparency than in standard economic models---transparency they argue that could be accomplished by blockchain technology. However, in their model, they assume entities can interact directly over private channels to arrange trades. They define front-running in the context of private offers, where one party might adjust their position before accepted or countering a received offer. This model is quite different than the concrete DApp-based model we study here.

>>>>

The second category of DApp in Table~\ref{tab:top25DApps} is crypto-collectables. Consider Cryptokitties~\cite{cryptokitties}, the most active DApp in this category and third most active overall. Each kitty (see Appendix~\ref{app:cryptokitty}) is a cartoon kitten with a set of unique features to distinguish it from other cryptokitties, some features are rarer and harder to obtain. They can be bought, sold, or bred with other cryptokitties. At the Ethereum level, the kitty is a token implemented with \textit{ERC-721: Non-Fungible Token Standard}~\cite{erc721}.

@@

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in the bids, but not the bid amounts. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name, \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Users are allowed to bid for 48 hours before the 48-hour reveal phase begins, in which bidders must send a transaction to reveal their bids for a specific domain. A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}. The auction model is similar to crypto-collectibles auctions in \ref{sec:cryptogames}.

@@

By tracing the transactions from these 30 addresses, we found explicit interference by F2Pool\footnote{F2Pool address was identified by their mining reward deposit address \url{https://etherscan.io/address/0x61c808d82a3ac53231750dadc13c777b59310bd9}.} in this scenario. As shown in Figure~\ref{fig:f2poolfront-run}, the funds deposited by F2Pool in these addresses were sent to \textit{Status.im} ICO and mined by F2Pool themselves, where the dynamic ceiling algorithm refunded a portion of the deposited funds. A few days after these funds were sent back to F2Pool main address and the tokens were aggregated later in one single address. Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their mining software to behave in a certain way to front-run other transactions by \textit{bulk displacement} to gain monetary profit.

@@

In the finance literature, Malinova and Park discuss front-running mitigations for blockchain-based trading platforms~\cite{malinova2017market}. Instead of studying DApps, they develop an economic model where transactions, asset holdings, and traders' identities have greater transparency than in standard economic models---transparency they argue that could be accomplished by blockchain technology. However, in their model, they assume entities can interact directly over private channels to arrange trades. They define front-running in the context of private offers, where parties might adjust their position before accepting or countering a received offer. This model is quite different than the DApp-based model we study here.
